
\chapter{Conclusions}

We can debate a lot of things in Computer Science but, in the end, the only
thing that matters is if we have accomplished our goals. Looking back at the
very beginning of this memoir we can read the main goal for this project:

\begin{quote}
\centering
  ``The goal of this project is to build a base platform that is able to
generate rich information about a set of cities in real time.''
\end{quote}

So, have we accomplished this goal? I think so. Looking back we can see
that during this project I have accomplished the following milestones:

\begin{enumerate}
  \itemsep0em
  \item I have created a base platform that processes data in streaming. The
base platform can be extended to fetch data from other sources, it can be
extended to handle the data in a different way, etc. This platform is
extensible and rock solid.
  \item I have implemented a couple of services that prove that this platform
works. The two services that have been developed in this project are quite
minimalistic, but they both prove that the base platform is working and that a
lot of things can be achieved with this software.
  \item I have explored the limits of this platform, and I have explained them
along the way. This way I have been capable to determine the requirements of
the platform. Moreover, with these tests I have been able to give some hints on
how a cluster can be built to run this platform.
\end{enumerate}

Therefore, I believe that all the expectations for this project have been
met, and I could not feel more confident about it.
