 
\section{The Budget}

\subsection{Estimated Salary}

The first thing to consider when computing the budget for a project is to
establish the wage for the people that will work on this project. In this
project I am alone, therefore I just have to compute my salary for the given
period of time that I have worked in this project.

So, what should I earn ? We have multiple possibilities when trying to
establish a wage for a job:

\begin{enumerate}
  \itemsep0em
  \item Spain has a minimum wage, so it is an option.
  \item We can pick the average salary for a Computer Programmer.
  \item We can pick the average salary for a Big data developer.
\end{enumerate}

The best option, in my opinion, is the second one. But since I also assumed the
role of the manager, I will assign myself the average salary of a computer
programmer in the USA, which is a bit higher than in Spain. According to
USNews\footnote{http://money.usnews.com/careers/best-jobs/web-developer/salary},
the average salary for a computer programmer in the USA was 74,280\$ anually in
2012. I believe that this quantity is fair. In euros this is 54,860.49\euro.

I am computing my salary by just multiplying the number of hours with the
\euro/hour rate. This salary does not include taxes. Here it goes:

\begin{center}
  54,860.49\euro{} anually $\Rightarrow$ 63.5 \euro/hour (18 hours/week as
explained in section \ref{sec:gep}) \\
  306 hours $\times$ 63.5\euro{} $\Rightarrow$ 19,431.0\euro{} in
{\bf total}
\end{center}

\subsection{Software}

Usually there are some costs associated with the software: licenses, patents,
etc. In my case the following are costs associated with software:

\mylist
  \item I have used the Archlinux\footnote{https://www.archlinux.org/} Linux
distribution as my Operating System. This Linux distribution is free of costs.
  \item All the libraries, frameworks, tools, etc. that I have used to build
the platform and the services around it are open source and free of costs. This
includes, for example, the following: the Storm framework, the Scala
programming language, KDevelop as my IDE, etc.
  \item I have written this memoir and all the delivered reports with \LaTeX{}
and the Kile editor. Both tools are open source and free of costs.
\mylistend

Therefore, I conclude that I have {\bf no} associated costs with the software
that I have used. Everything that I have used is open source and free of costs.

\subsection{Hardware}

I have only used my laptop to go through this Thesis. I would not usually
consider it as a cost, but it is an established practice when computing the
costs of a project. This is to cover any incident that can happen to my laptop
when developing this project. Lucky for me, my laptop has not suffered any
damage. Anyways, we have to compute it.

My laptop is an Apple Macbook Air from late 2013 (with an extra of RAM). I paid
around 1400\euro{} for this laptop. Since I have a warranty for 2 years, I will
divide these 1400\euro between 24 months. Therefore:

\begin{center}
  1400\euro{} / 24 months = 116.66\euro{}/month \\
  116.66\euro{} $\times$ 4 months = 466.64\euro{} in {\bf total}.
\end{center}


\subsection{Conclusions}

My main conclusion is that all the costs of this project are tied to the people
that is working on it. In this case, I am alone, and therefore, the costs of
this platform can only be computed as the time that I have spent working on it.

Specifically, the costs are my salary and the amortized cost of my laptop. Note
though that this result does not include taxes. With everything being computed,
I conclude that the budget for this project is:

\begin{center}
  19,431.0\euro{} + 466.64\euro{} = {\bf 19,897.64\euro{} in total}.
\end{center}
