
\section{Goals and Motivations}

\subsection{Goals}

Before going any further, it is important to write down the goals of this
project. It is important because this way:

\begin{enumerate}
  \itemsep0em
  \item We can determine if the project has been successful.
  \item We can focus on just these goals and not get distracted by other topics.
\end{enumerate}

My goals for this project have been clear since the very start of this project.
More importantly, I think that I have accomplished these goals, and thus I can
feel satisfied about this project. Without further due, the following are my
goals for this project:

\mylist
  \item Design the {\bf base platform}. That is, to build the basic
infrastructure in which the rest of the code will be based on.
  \item Design a couple of useful {\bf services} showing the potential of this
platform.
  \item Give some hints on the design of an ideal {\bf cluster} that can run
this platform.
\mylistend

The first two points have been explained throughout the sections
\ref{sec:overview} and \ref{sec:implementation}. These two section explain
how I have designed and implemented the platform. After reading these two
sections it will be clear that these two points have been successfully
completed. The last point has been explained in the section \ref{sec:cluster}
of this memoir.

\subsection{Motivations}

I think it is also important to write down my motivations for doing this
project. The following are my reasons for doing this:

\mylist
  \item {\bf Research}. Because of my Thesis, I will be doing a lot of
research. My main focus of research has been: Big data, streaming processing and
smart cities.
  \item {\bf Learn} some technologies as a side effect. My base technology has
been the Storm framework, which is done in Java. The platform that I have done
that lies on top of it has been done in Scala. Therefore, I have improved my
skills in the Java and the Scala programming languages.
  \item {\bf Provide} a useful technology base. Even if this platform has
been designed to solve a specific problem, I am confident that it can be
useful for other people interested in the technology. Moreover, this platform
can potentially help european cities, specifically Barcelona in my case. And
more than that, I am really optimistic about this platform because I believe
that it can be the base for other thesis of other students.
  \item {\bf Practice}. The Bachelor Degree Thesis is the final stop of this
journey that I've been doing in the Barcelona School of Informatics. I've
learnt a lot and I have applied some of the concepts learnt in this
university to this Thesis.
\mylistend

