
\section{Budget}

\subsection{Introduction}

In this delivery I am focusing on the budget and on the impact of my project.
First of all, I am going to focus on the budget. This includes doing some math
in the following topics: human resources, hardware and software.

Lastly, I will be explaining the impact that I expect that this project will
have. My only considerations for the impact will be the social impact and the
environmental impact.

\subsection{Budget}

In this section I will be describing the estimated costs that this project will
have. After specifying each of the costs, I will make up a total amount of
estimated costs. This will lead me to conclude the needed budget for this
project.

\subsection{Human resources}

In my humble opinion the words ``human resources'' are quite awful, since it
feels like we are treating people like objects. Far from that, what I want to
do in this section is to describe all the costs related to employing people to
develop this project.

Luckily enough, it is just me in this project, so I just have to computemy own
salary. After doing some research, I have found that the average salary for a
Big data analyst is around 99,000 USD a year. This boils down to 51 USD per
hour. I did my scheduling based on weeks, instead of hours, and I think that I
will spend 20 hours in average per week. This means that in total, my salary
during the project will be:

\[
  20\ hours \cdot 16\ weeks \cdot 51\ USD = 16,320\ USD
\]


\subsection{Hardware}

Ideally in this section I would explain all the costs regarding the hardware.
However, I can't compute this because the only hardware that I will specify will
be the cluster which, in turn, is just a proposal. Other things like my laptop
won't be counted in this section They are not a cost for this project since I
use them for personal purposes too.

\subsection{Software}

In this section I will describe all the costs associated with software. In
short, this is my budget for software:

\[
  0\ \$
\]

All the software that I will be using for this project is free: both as in
``free beer'' as in ``free speech''. There are no fees for any license, I won't
be using any paid service, etc. Nothing.

\subsection{Total}

The main conclusion is that the only cost associated to this project is just my
salary. Therefore, my estimated costs are a total of \$16,320.

\subsection{Social impact}

This section is really important for this project. It is about the impact that
this platform will make to society. This is not a direct impact, but an
indirect one. The social impact of this platform comes in two ways:

\mylist
  \item The fact that a number of businesses will take advantage that this
platform exists.
  \item Indirectly, all the impact that all the services built on top of this
platform will produce.
\mylistend

This means that, ideally, the social impact of this platform can be huge.

\subsection{Environmental impact}

In the same way that this platform can bring a lot of goodness in the social
front, it certaintly comes with a cost. In my case the cost is an environmental
impact that cannot be understated.

In this project I will propose an ideal cluster that would be able to run the
software that I will design. The problem here is that maintaining a cluster
means the following:

\mylist
  \item Power supply.
  \item Maintaining a cooling system.
  \item The implied environmental costs of building the cluster.
\mylistend

All of these can be reduced by using the minimum amount of cluster time as
possible. This means to run the software in ``batches'' or with a very low
latency. However, this is not possible at all if the cluster has a lot of
requests, and that is to be expected.

Therefore, in the development of the cluster I will focus most of my efforts
into keeping the cluster as environmental friendly as possible.
