
\section{Introduction}

\subsection{Context}

This is the final report of the GEP course. The GEP course is part of my
Bachelor Degree Thesis, and consists of a set of deliveries and instructions
that has helped me in the preparation of my Thesis.

My Bachelor Degree Thesis is being presented at the Barcelona School of
Informatics and is directed by Mr. Jordi García Almiñana. The project was
originally envisioned by the director, and the author must develop a solution
for the given problem.

\subsection{Brief project description}

My Bachelor's Degree Thesis is about building an infrastructure that is
capable of providing a set of services from the data that has been collected
and processed. This data will come from initiatives like OpenData BCN and
iCity. This infrastructure will fetch and process all this data in realtime,
by using a set of new technologies that allow us to do so.

\subsection{Brief state of the art}

Since the appearence of the MapReduce algorithm, a lot of different
technologies have evolved so we can now fetch and process huge amounts of data.
This is important for the computer industry, but also for governments and other
associations.

We have a huge list of technologies that deal with Big data, but maybe the more
important ones are Hadoop and Storm. Storm is the base technology that I will be
using in this project. It's a modern and mature framework that will allow me to
build a realtime pipeline that is capable of fetching and processing huge
amounts of data.

\subsection{Purpose}

The purpose of this project is to provide a base infrastructure capable of
fetching and processing large amounts of data from iniciatives like OpenData
BCN and iCity to provide a set of services improving the actual situation.
