
\documentclass[a4paper,12pt]{article}

\usepackage{indentfirst}
\usepackage[pdftex]{graphicx}
\usepackage{wrapfig}
\usepackage[utf8]{inputenc}
\usepackage[catalan]{babel}

\newcommand{\espai}{\par\vspace{5mm}}
\newcommand{\mylist}{
\begin{itemize}
\setlength{\itemsep}{1pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}}
\newcommand{\mylistend}{\end{itemize}}

\usepackage{titling}
\setlength{\droptitle}{-5cm}

\begin{document}

% Title
\title{Scope of my Bachelor's Degree Thesis}
\author{Miquel Sabaté Solà}
\date{20th February 2014}
\maketitle

\setcounter{page}{1}

\vspace{-1.0cm}

\section*{Introduction}

\subsection*{The context: Big data and streaming}

Once upon a time, Google released a paper called:
``MapReduce: Simplified Data Processing on Large
Clusters''\footnote{http://research.google.com/archive/mapreduce-osdi04.pdf}.
This was the beginning of a revolution in the data processing front. After
that, lots of efforts have been put in this direction, being Hadoop one of the
most important accomplishments. Hadoop (and related technologies) has made it
possible to store and process data at scales previously unthinkable.

However, these technologies have one major drawback: they are not realtime
systems, nor are they meant to be. In order to solve this issue one has to
manually implement a network of queues and workers. These worker would
eventually send messages, update databases, and send new messages to other
queues for further processing. This, of course, has some serious limitations:
it's tedious, it doesn't scale, and it has little fault-tolerance.

In order to fix the previously cited issues from the core, some projects like
Yahoo! S4 and Twitter Storm emerged. Both projects have some differences but
they have a clear focus: to ease the writing of parallel realtime computation.
Sadly, nowadays the S4 project is dead. This is why in this thesis I'm picking
Storm\footnote{http://storm-project.net} as the base technology (plus, the Storm
project has a very active community).

\subsection*{Scope of my proposal}

My Bachelor's Degree Thesis is about building an infrastructure that is capable
of providing a set of services from the data that has been collected and
processed. The raw data for this infrastructure will come from OpenData
BCN\footnote{http://opendata.bcn.cat/opendata/en} iniciative. That is, the
infrastructure that I'm going to build for my thesis will provide additional
features to the OpenData BCN iniciative that are only possible by building a
cluster that will process data continiously.

This infrastructure will fetch and process all this data in realtime, using
Storm as the base technology in the software front. This is important because
the users of all the services build upon these infrastructure will be able to
fetch all the processed data also in realtime.

This means that I'm not just going to do research only in the Big data and
streaming front, but I'm also going to get my hands dirty with the whole concept
of ``Smart City''. This is because this infrastructure will be built in a way
so other services can fetch our processed data to improve, promote and have a
better understanding of the city of Barcelona.

This is my proposal. However, any proposal is doomed if it's not specified a set
of rules that define the scope of it. The scope of my Thesis will consist of
the following points:

\mylist
  \item Design a cluster that can match our requirements.
  \item Design a base system that will fetch and process all the data.
  \item Provide a couple of useful services on top of the base system.
\mylistend

\section*{Goals}

The previous section contained all the information regarding what my Thesis is
about. Now I'm going to relate my goals for doing this project.

\mylist
  \item {\bf Research}. Because of this thesis, I'll be doing a lot of
research. My main focus will be: Big data, streaming processing and smart
cities. I will be investigating, for each of them, their state of the art, what
should we know about and what can we do with them.
  \item {\bf Learn} some technologies as a side effect. My base technology will
be the Storm framework. This means that I'll be learning and improving my
skills in programming languages like Java and Scala. I will also be improving my
skills with concurrent programming. I'll further also my knowledge on hardware
by analyzing what kind of machines we need in order to provide and scale all the
services.
  \item {\bf Provide} a useful technology base. The main goal of this Thesis is
to create a base technology that will be useful to other people. This way we'll
be able to provide a set of services that will potentially improve the city of
Barcelona on multiple ways. I'm really optimistic about this project, and I can
see other thesis from other students about improving or extending the
infrastructure that I'll be building in my thesis.
  \item {\bf Practice}. The Bachelor's Degree Thesis is the final stop of this
journey that I've been doing in the Barcelona School of Informatics. I've
learnt a lot and I'm ready to apply some of the concepts learnt in this
university to this Thesis.

\mylistend

\section*{About the development}

Lastly, I want to clarify how I want to develop this project. First of all, the
code that will make all this to happen is open source. This means that all of
the base technology and the code that I will be developing is all open source.
In fact, all my code is hosted on
Github\footnote{https://github.com/mssola/thesis}. This is really important for
me for the following reasons:

\mylist
  \item I'm a strong advocate of Open Source.
  \item It could help future thesis based on this infrastructure.
  \item It could help anyone in the world that is developing something similar.
  \item It's fair.
\mylistend

My workflow will consist in discussing any doubts that I'd have with my teacher
and keep on developing the whole platform in an open way. Finally, I want to
point out my resources, that I quite humble. I'll spend most of my time doing
this project, with all the resources that I have.

\end{document}
